Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-08 Manuscript/manuscript.tex

Ion density profiles from simulations with different models are compared in Fig.~\ref{fig:cacl-dens}.
The density profiles from simulations with original Lipid14 \cite{dickson14} and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
or the standard Amber ion model by \AA{qvist}~\cite{aqvist90}
along with Lipid14 does not significantly change it 
(Headgroup order parameter responses for these models in SI).
\todo{Add OP-response of Lipid14+ECC-ions into the OP-changes plot in SI}
The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16} exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
Together with the accurate head group order parameter response (Fig.~\ref{OrderParameterCHANGESnewMODELS}),
we can conclude that the present model, ECC-lipids, exhibits accurate ion binding affinity to zwitterionic phospholipid membranes
suggesting that the models that overestimate head group order parameter response~\cite{catte16} also overestimate the amount of bound cations.

>>>>

Based on the accurate head group order parameter response of the new model, ECC-lipids, (Fig.~\ref{OrderParameterCHANGESnewMODELS})
we suggest that it also exhibits accurate ion binding affinity to zwitterionic phospholipid membranes.
This is directly related to the amount of surface excess charge 
as shown along with ion density profiles in Fig.~\ref{fig:cacl-dens}.
The density profiles from simulations with original Lipid14 \cite{dickson14} and Dang ions \cite{smith94,chang1999,dang2006} 
show a pronounced peak in the position of the phosphate moieties of POPC. 
The use of a ECC-ion model~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16}
or the standard Amber ion model by \AA{qvist}~\cite{aqvist90}
along with Lipid14 does not significantly change it 
(Headgroup order parameter responses for these models in SI).
\todo{Add OP-response of Lipid14+ECC-ions into the OP-changes plot in SI}
The new ECC-lipids model with ECC-ions~\cite{Jungwirth2017,Jungwirth2015,kohagen14,kohagen16} exhibits on the other hand smaller density in this region 
suggesting overall weaker binding of cations (Fig.~\ref{OrderParameterCHANGESnewMODELS}). 
It is then likely that the models that overestimate head group order parameter response~\cite{catte16} also overestimate the amount of bound cations.
